Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-18 ms.tex
beginning re-write of likelihood and uncertainty budget explanations

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}
\usepackage{mathrsfs}

@@

With these color corrections and the  formalism established in 
$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
use e.g. during MCMC sampling to predict the observed SED, which we will 
denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:

@@

In our full-resolution fits, we use a MCMC approach to constrain the 
parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
Metropolis-Hastings (MH) Markov chain sampling the posterior probability of
reproducing the observed 217-3000 GHz SED as a function of the two parameters 
$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
given by:

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here $\vec{I}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{I}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
$I_{857}$, $I_{3000}$). The likelihood function is given by:

\begin{equation} \label{equ:like}
\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
\end{equation}

@@

Where the product runs over $\nu_i$$\in$$\{217,\ 353,\ 545,\ 857,\ 3000\}$ GHz
and $\tilde{I}_{\nu_i}$ is a function of $\tilde{I}_{545}$ and $T_2$ as 
specified by Equation \ref{eqn:inten}. For each pixel, the uncertainty on each 
intensity measurement $\sigma_{\nu_i}$ is given by:

\begin{equation}
\sigma_{\nu_i}(p) = \sqrt{c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2}
\end{equation}

>>>>

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{amsmath}

@@

With these color corrections and the  formalism established in 
$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
use e.g. during MCMC sampling to predict the observed SED. The predicted 
observation in band $\nu_i$ is given by:

@@

In our full-resolution fits, we use a MCMC approach to constrain the 
parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
Metropolis-Hastings (MH) Markov chain sampling the posterior probability of
the observed 217-3000 GHz thermal dust SED as a function of the two parameters 
$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
given by:

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\vec{\mathbf{I}}~) \propto \mathcal{L}(\vec{\mathbf{I}}~|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

Here $\vec{\mathbf{I}}$ denotes the vector of observed thermal dust intensities quoted 
under the `IRAS convention': $\vec{\mathbf{I}}$ = ($I_{217}$, $I_{353}$, $I_{545}$, 
$I_{857}$, $I_{3000}$). The likelihood function is given by:

%\begin{equation} \label{equ:like}
%\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \displaystyle\prod\limits_{i}\mathcal{N}(\tilde{I}_{\nu_{i}}|I_{\nu_{i}}, \sigma_{\nu_i})
%\end{equation}

\begin{equation} \label{equ:like}
\mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})\Sigma^{-1}(\vec{\mathbf{I}}-\underline{\mathbf{\tilde{I}}})^T\Big]
\end{equation}

@@

Here $\underline{\mathbf{\tilde{I}}}$ is the vector of predicted observations 
based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
and $T_2$: $\underline{\mathbf{\tilde{I}}} = $($\tilde{I}_{217}$, 
$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
observed intensities:

\begin{equation}
\Sigma = \begin{pmatrix} \sigma^2_{217}                           & \ldots  & \rho_{217,3000}\sigma_{217}\sigma_{3000} \\ 
                         \vdots                                   & \ddots  & \vdots                                   \\
                         \rho_{3000,217}\sigma_{3000}\sigma_{217} & \ldots  & \sigma^2_{3000}
\end{pmatrix}
\end{equation}

For each pixel $p$ and band $\nu_i$, the variance of the measured value 
$I_{\nu_i}(p)$ is taken to be:

\begin{equation}
\sigma_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2
\end{equation}
